---
title: "ST503 HW1 SHAN YANG"
output:
  word_document: default
  html_notebook: default
---

##2.4##
```{r}
library(faraway)
data<-prostate
head(prostate)
```
get the regression of each variables added in 
```{r}
olca<-lm(lpsa~lcavol,data=prostate)
olwei<-lm(lpsa~lcavol+lweight,data=prostate)
osvi<-lm(lpsa~lcavol+lweight+svi,data=prostate)
olbph<-lm(lpsa~lcavol+lweight+svi+lbph,data=prostate)
oage<-lm(lpsa~lcavol+lweight+svi+lbph+age,data=prostate)
olcp<-lm(lpsa~lcavol+lweight+svi+lbph+age+lcp,data=prostate)
opgg<-lm(lpsa~lcavol+lweight+svi+lbph+age+lcp+pgg45,data=prostate)
oglea<-lm(lpsa~lcavol+lweight+svi+lbph+age+lcp+pgg45+gleason,data=prostate)
```
get their standard errors for residuals
```{r}
sd<-c(summary(olca)$sigma,summary(olwei)$sigma,summary(osvi)$sigma,summary(olbph)$sigma,summary(oage)$sigma,summary(olcp)$sigma,summary(opgg)$sigma,summary(oglea)$sigma)
##Can not use sd(lm$residuals), the df is wrong
##Same as sqrt(deviance(oglea)/df.residual(oglea))

#get the r-squares for regression
rsquared<-c(summary(olca)$r.squared,summary(olwei)$r.squared,summary(osvi)$r.squared,summary(olbph)$r.squared,summary(oage)$r.squared,summary(olcp)$r.squared,summary(opgg)$r.squared,summary(oglea)$r.squared)
```
plot the trend

```{r}
par(mfrow=c(1, 2))
plot(sd,main="Trend for standard error when adding in variables",xlab="number of variables",ylab="sd for e",type="l")
plot(rsquared,main="Trend for R-sq when adding in variables",xlab="number of variables",ylab="R-sq",type="l")
```
##2.6
```{r}
cheddar<-cheddar
head(cheddar)
```
(a)Regression and get the coefficients
```{r}
ocheddar<-lm(taste~Acetic+H2S+Lactic,data=cheddar)
ocheddar
```
(b)get the corr and square it
```{r}
fittedy<-ocheddar$fitted.values
corsq<-cor(x=cheddar$taste,y=fittedy)^2
corsq
```
```{r}
summary(ocheddar)
```
So the corr-sq is the Multiple R-squared in the regression.

Problem 4(b). Regression through the origin, Hubble data

x is the distance from earth, y is the v of a galaxy
```{r}
x <- c(0.032, 0.034, 0.214, 0.263, 0.275, 0.275, 0.450, 0.500, 0.500, 0.630, 0.800, 0.900, 
       0.900, 0.900, 0.900, 1.000, 1.100, 1.100, 1.400, 1.700, 2.000, 2.000, 2.000, 2.000)
y <- c(170, 290, -130,-70, -185, -220, 200, 290, 270, 200, 300, -30,  
       650, 150, 500, 920, 450, 500, 500, 960, 500, 850, 800, 1090)
```

```{r}
ohubble<-lm(y~0+x) #do the regression and force it go through the origin
plot(x,y,xlab = "Distance from earth",ylab = "v of galaxy",main = "Regression thourgh origin") #get the scatter plot
abline(ohubble) #add regression line to it
```
```{r}
fittedv<-ohubble$fitted.values
cor(y,fittedv)^2
```
We can read the correlation is .6235, which means a relatively strong positive relationship between distance and velocity

5.
```{r}
n <- 15
op <- par(pty="m", mfrow=c(3, 3), mar=c(4.2, 4.2, 1, 1))
for(i in 1:9) {
  
  X <- rnorm(n)
  hist(X, freq=FALSE, col="gray", border="white", main="")
  curve(dnorm(x, mean(X), sd(X)), add=TRUE)
  
}
par(op)
```
4 of them are kind or "normal". The first one is right-skewed, the second is approximately normal but with really heavy tail, third has two "tops", forth is almost normal, fifth also has two tops, sixth right-skewed, seventh seems normal, eighth almost normal, ninth almost normal.
